---
title: "Quarto_Paper_MaC"
format: html
editor: visual
---

# Democracy and social media: Between the dialogue and the strategy

Andrés Scherman^1^, Pedro Fierro^2^ and Leo Yuanliang Shan^3^

^1^ LEAS at School of Communication and Journalism, Universidad Adolfo Ibáñez.

^2^ Business School, Universidad Adolfo Ibáñez; and Department of Media and Communication, London School of Economics.

^3^ School of Journalism and Mass Communication, University of Wisconsin-Madison.

## Abstract

This study analyzes the role of traditional news media and social media in public deliberation within democratic systems. Using the concepts of Understanding Orientation (consensus-oriented, communicative rationality) and Strategic Orientation (goal-oriented, instrumental rationality), proposed by Jürgen Habermas, this study looks at the public space in a digital context to explore how the news media can either contribute to the existence of rational communication in the public debate or, conversely, promote interventions of a strategic nature. To estimate the influence of traditional news media and social media on the orientation to engage in dialogue with others within a framework of rationality and equality, this study relies on a two-wave online panel survey conducted in Chile before and after the constitutional referendum, held on September 4, 2022, a period of intense political polarization. The first wave (T1) received 2,117 responses, and the second wave (T2) received 903 responses. Results show that Understanding Orientation is a predictor of political situations linked to public deliberation, such as Political Participation and Political Interest. However, news consumption in both traditional news outlets and social media is not associated with the presence of Understanding Orientation, but rather with Strategic Orientation. These results support a more pessimistic view of the contribution of the news media and social media to creating a rational public sphere, where reason should predominate in interactions between citizens to strengthen democracy.

## Methodology

### Data

The data for this study was obtained from a national survey conducted in Chile under the supervision of the Millennium Nucleus for the Study of Politics, Public Opinion, and Media in Chile (Nucleo MEPOP). The complete survey consisted of three waves, but this study only utilizes data from the first and third waves. Wave 1 was conducted between August 25 and September 8, while Wave 3 was conducted between \[insert dates\]. The total sample size for this analysis was 950 individuals, specifically those who participated in both Wave 1 and Wave 3.

It is important to note that the survey instrument did not necessarily include the same questions across all three waves. As a result, the analyses presented in this paper are cross-sectional in nature. While the dependent variable was constructed from responses in Wave 3, all independent variables were drawn from Wave 1. The survey design employed quotas based on gender, age, and socioeconomic level, ensuring alignment with national distributions.

```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}

# clean workspace
rm(list=ls())

options(scipen=999, # avoid scientific notation
        stringsAsFactors = FALSE, digits = 2)

options(digits = 7)

library(haven)
library(knitr)
library(lattice)
library(tidyverse)
library(here)
library(flextable)
library(devtools)
library(lavaan)
library(ggplot2)
library(plm)
library(naniar)
library(purrr)
library(psych)
library(interactions)
library(semPlot)
library(coefplot)
```

```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
#Import Data
data_w1 <- read_sav("Data_W1.sav")

# ID
data_w1$id <- data_w1$CodPanelista

#Import Data
data_w3 <- read_sav("Data_W3.sav")

# ID
data_w3$id <- data_w3$CodPanelista

```

### Variables

#### Understanding orientation:

Following the previously mentioned literature, understanding orientation was measured by asking respondents to indicate how much they agree or disagree with the following statements:

Under1: "In political conversations, it is essential to listen carefully to what others have to say."

Under2: "When I talk about politics, learning is more important to me than convincing."

Under3: "Through my conversations, I promote solidarity with others."

Under4: "At its core, politics aims to reach agreements through conversation."

Under5: "When I talk about politics, I feel connected to the people I talk with."

Under6: "Through conversation, political interests can be directed toward the common good."

Under7: "Talking about politics allows me to understand why others see things differently."

Under8: "Political conversations are important for protecting people's rights."

All responses were measured on a 5-point Likert scale, where 1 indicated strong disagreement and 5 indicated strong agreement. A factor was constructed using the eight responses (α = 0.86).

#### Strategic Orientation

Similarly, to measure strategic orientations, all respondents were asked to indicate how much they agree or disagree with the following statements:

Strate1: "Saying one thing while thinking another is fundamental when talking about politics."

Strate2: "I talk about politics if I gain something from it."

Strate3: "In political conversations, form is more important than content."

Strate4: "When talking about politics, it is sometimes better not to express what you truly think."

Strate5: "People are tired of being asked to talk in order to reach political agreements."

Strate6: "The head of the household decides and does not need to reach an agreement with other family members."

Strate7: "Instead of so much discussion, it's better for someone to just say how things are."

Strate8: "Trying to reach agreements through conversation is a waste of time; it's better if someone decides what to do and gets it done."

All responses were measured on a 5-point Likert scale, where 1 indicated strong disagreement and 5 indicated strong agreement. A factor was constructed using the eight responses (α = 0.75).

#### Political Efficacy

In line with the literature, political efficacy was divided into three distinct dimensions. First, external efficacy---i.e., beliefs about system responsiveness---was measured using the following statements:

extef1: "Politicians don't really care about what voters think."

extef2: "Politicians waste a lot of taxpayers' money."

extef3: "People like me have no influence over what is decided in parliament or government."

Similarly, internal efficacy---self-competence beliefs---was measured with the following statements:

intef1: "In general, I don't find it difficult to take a stance on political issues."

intef2: "People like me are qualified to participate in political discussions."

intef3: "People like me have political opinions that are worth listening to."

Finally, following recent literature, an additional set of questions was used to measure online political efficacy---i.e., the belief that, because of the Internet, it is possible to have more influence on politics and public issues:

ope1: "Using the internet, people like me have more political power."

ope2: "Using the internet, I can have more say over what the government does."

ope3: "Using the internet, it is easier for me to understand politics."

ope4: "Using the internet, public officials care more about what I think."

All responses were measured on a 5-point Likert scale, where 1 indicated strong disagreement and 5 indicated strong agreement. A factor was created for each of the dimensions (external efficacy: α = 0.74; internal efficacy: α = 0.74; online political efficacy: α = 0.84).

#### Political Interest

To measure political efficacy respondents were asked to .... 

#### Media Exposure

#### Sociodemographic Variables

Additionally, we controlled the models by incorporating various sociodemographic variables. These included education level, sex (mean = 0.45, where 0 = male and 1 = female), socioeconomic status (range: 1 to 5, mean = 3.2), and age (range: 18 to 84, mean = 44.91).

```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
# Age
data_w1$age_num <- data_w1$age

# Socioeconomic Status
data_w1$ses <- data_w1$RECO_NSE

# Education
data_w1$educ <- data_w1$P60

# Sex (1=women)
data_w1 <- data_w1%>%
  mutate(sex = ifelse(SEX == 2, 1,
                      ifelse(SEX == 1, 0, NA)))

# Ideology
data_w1$ideology <- ifelse(data_w1$P32 == 99, NA, data_w1$P32)

# Online Political Efficacy
data_w1$ope1 <- data_w1$P59_1
data_w1$ope2 <- data_w1$P59_2
data_w1$ope3 <- data_w1$P59_3
data_w1$ope4 <- data_w1$P59_4

# External Political Efficacy (recode)
data_w1$extef1 <- data_w1$P58_1
data_w1$extef2 <- data_w1$P58_2
data_w1$extef3 <- data_w1$P58_3

# To recode efficacies (intef1, intef3, extef1, extef3, extef4)
data_w1 <- data_w1 %>%
  mutate(across(c(extef1, extef2, extef3), ~ 6 - .x))

# Internal Political Efficacy
data_w1$intef1 <- data_w1$P58_4
data_w1$intef2 <- data_w1$P58_5
data_w1$intef3 <- data_w1$P58_6

# Media Exposure
data_w1$tv <- data_w1$P4_1
data_w1$cable <- data_w1$P4_2
data_w1$newspaper <- data_w1$P4_3
data_w1$radio <- data_w1$P4_4
data_w1$tradonline <- data_w1$P4_5
data_w1$online <- data_w1$P4_6
data_w1$podcast <- data_w1$P4_7
data_w1$officialsm <- data_w1$P4_8

# Social Media Exposure
data_w1$fb <- ifelse(data_w1$P5_1 == 99, NA, data_w1$P5_1)
data_w1$insta <- ifelse(data_w1$P5_2 == 99, NA, data_w1$P5_2)
data_w1$twitter <- ifelse(data_w1$P5_3 == 99, NA, data_w1$P5_3)
data_w1$whatsapp <- ifelse(data_w1$P5_4 == 99, NA, data_w1$P5_4)
data_w1$youtube <- ifelse(data_w1$P5_5 == 99, NA, data_w1$P5_5)
data_w1$tiktok <- ifelse(data_w1$P5_6 == 99, NA, data_w1$P5_6)
data_w1$discord <- ifelse(data_w1$P5_7 == 99, NA, data_w1$P5_7)
data_w1$twitch <- ifelse(data_w1$P5_8 == 99, NA, data_w1$P5_8)

# Franja Exposure
data_w1$franja <- data_w1$P6_1

# Social Media Political Use
data_w1$use1 <- data_w1$P25_5
data_w1$use2 <- data_w1$P25_6
data_w1$use3 <- data_w1$P25_7
data_w1$use4 <- data_w1$P25_8
data_w1$use5 <- data_w1$P25_9
data_w1$use6 <- data_w1$P25_10
data_w1$use7 <- data_w1$P25_11

# Interest
data_w1$polint <- data_w1$P21
data_w1$procint <- data_w1$P22
data_w1$plebint <- data_w1$P23

# Interpersonal confidence
data_w1 <- data_w1%>%
  mutate(intercon = ifelse(P51 == 2, 1,
                      ifelse(P51 == 1, 0, NA)))

#Understanding orientation
data_w1$under1 <- data_w1$P48_1
data_w1$under2 <- data_w1$P48_4
data_w1$under3 <- data_w1$P48_5
data_w1$under4 <- data_w1$P48_7

#Strategic orientation
data_w1$strate1 <- data_w1$P49_2
data_w1$strate2 <- data_w1$P49_3
data_w1$strate3 <- data_w1$P49_4
data_w1$strate4 <- data_w1$P49_8

##### Data from wave 3

#Understanding orientation
data_w3$under_w3_1 <- data_w3$P48_1
data_w3$under_w3_2 <- data_w3$P48_2
data_w3$under_w3_3 <- data_w3$P48_3
data_w3$under_w3_4 <- data_w3$P48_4
data_w3$under_w3_5 <- data_w3$P48_5
data_w3$under_w3_6 <- data_w3$P48_6
data_w3$under_w3_7 <- data_w3$P48_7
data_w3$under_w3_8 <- data_w3$P48_8

#Strategic orientation
data_w3$strate_w3_1 <- data_w3$P49_1
data_w3$strate_w3_2 <- data_w3$P49_2
data_w3$strate_w3_3 <- data_w3$P49_3
data_w3$strate_w3_4 <- data_w3$P49_4
data_w3$strate_w3_5 <- data_w3$P49_5
data_w3$strate_w3_6 <- data_w3$P49_6
data_w3$strate_w3_7 <- data_w3$P49_7
data_w3$strate_w3_8 <- data_w3$P49_8

```

```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
# Assuming 'id' is your key variable for merging
data_w3_selected <- data_w3 %>%
  select(id, starts_with("strate_w3_"), starts_with("under_w3_")) %>%
  drop_na()

data_w1_na <- na.omit(data_w1[c("id", "polint", "procint", "plebint", "ope1", "ope2", "ope3", "ope4", "intef1", "intef2", "intef3", "extef1", "extef2", "extef3", "intercon", "tv", "cable", "newspaper", "radio", "tradonline", "online", "podcast", "officialsm","fb", "insta", "twitter", "whatsapp", "youtube", "tiktok", "age_num", "ses", "sex", "educ")])
sum(is.na(data_w1_na))

# Merge dataframes
merged_data <- data_w1_na %>%
  left_join(data_w3_selected, by = "id") %>%
  drop_na()

```


```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
cronbach_ope <- alpha(na.omit(merged_data[c("ope1", "ope2", "ope3", "ope4")]))
cronbach_ope

cronbach_intef <- alpha(na.omit(merged_data[c("intef1", "intef2", "intef3")]))
cronbach_intef

cronbach_extef <- alpha(na.omit(merged_data[c("extef1", "extef2", "extef3")]))
cronbach_extef

cronbach_media <- alpha(na.omit(merged_data[c("tv", "cable", "newspaper", "radio")]))
cronbach_media

cronbach_digital <- alpha(na.omit(merged_data[c("tradonline", "online", "podcast", "officialsm")]))
cronbach_digital

cronbach_social <- alpha(na.omit(merged_data[c("fb", "insta", "twitter", "whatsapp", "youtube", "tiktok")]))
cronbach_social

cronbach_interest <- alpha(na.omit(merged_data[c("polint", "procint", "plebint")]))
cronbach_interest

cronbach_under <- alpha(na.omit(merged_data[c("under_w3_1", "under_w3_2", "under_w3_3", "under_w3_4", "under_w3_5", "under_w3_6", "under_w3_7", "under_w3_8")]))
cronbach_under

cronbach_strate <- alpha(na.omit(merged_data[c("strate_w3_1", "strate_w3_2", "strate_w3_3", "strate_w3_4", "strate_w3_5", "strate_w3_6", "strate_w3_7", "strate_w3_8")]))
cronbach_strate

```

### Analysis

To test our hypothesis, the analysis was divided into two parts. First, different factors were created for the variables described in the previous section using Confirmatory Factor Analysis (CFA). We chose this technique because the selection of variables was theoretically grounded and supported by previous literature. Figures 1, 2, and 3 present the measurement models for the nine factors we developed.

```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}

merged_data <- merged_data %>%
  mutate(across(where(is.labelled), as.numeric))

cfa.model1 <- 'ope =~ ope1 + ope2 + ope3 + ope4
              intef =~ intef1 + intef2 + intef3
              extef =~ extef1 + extef2 + extef3
              interest =~ polint + procint + plebint'
cfa.model2 <- 'media =~ tv + cable + newspaper + radio
              digital =~ tradonline + online + podcast + officialsm
              social =~ fb + insta + twitter + whatsapp + youtube + tiktok'
cfa.model3 <- 'under =~ under_w3_1 + under_w3_2 + under_w3_3 + under_w3_4 + under_w3_5 + under_w3_6 + under_w3_7 + under_w3_8
              strate =~ strate_w3_1 + strate_w3_2 + strate_w3_3 + strate_w3_4 + strate_w3_5 + strate_w3_6 + strate_w3_7 + strate_w3_8'

fit_cfa1 <- cfa(cfa.model1, data = merged_data)
latent_scores1 <- predict(fit_cfa1)

fit_cfa2 <- cfa(cfa.model2, data = merged_data)
latent_scores2 <- predict(fit_cfa2)

fit_cfa3 <- cfa(cfa.model3, data = merged_data)
latent_scores3 <- predict(fit_cfa3)

merged_data <- cbind(merged_data, latent_scores1, latent_scores2, latent_scores3)
```

**Figure 1** Measurement Model for Political Efficacies

```{r echo=FALSE, message=FALSE, warning=FALSE}
semPaths(fit_cfa1, "std", layout = "tree", rotation = 2,
         whatLabels = "std", edge.label.cex = 0.8,
         sizeMan = 3, sizeLat = 7, title = TRUE)
```
Note: Own elaboration.

**Figure 2** Measurment model for Media Exposure
```{r echo=FALSE, message=FALSE, warning=FALSE}
semPaths(fit_cfa2, "std", layout = "tree", rotation = 2,
         whatLabels = "std", edge.label.cex = 0.8,
         sizeMan = 3, sizeLat = 7, title = TRUE)
```
Note: Own elaboration.

**Figure 3** Measurment model for understanding and strategic orientations
```{r echo=FALSE, message=FALSE, warning=FALSE}

semPaths(fit_cfa3, "std", layout = "tree", rotation = 2,
         whatLabels = "std", edge.label.cex = 0.8,
         sizeMan = 3, sizeLat = 7, title = TRUE)
```
Note: Own elaboration.

The second part of the analysis explored which variables might be related to the propensity for having an understanding or strategic orientation toward political interactions, using traditional OLS regressions. We recognize that, given the nature of our data and the design of the analysis, Structural Equation Modeling (SEM) could be a more appropriate method to test these interactions. The advantage of SEM is that it allows us to create latent factors from observable variables—as we did—and simultaneously test the interactions between variables in the model. Thus, to ensure the robustness of our results, we also applied SEM for the two orientations under studied. These results, which are presented in the appendix, are consistent with the findings described in the following section.

### Results

**Table 1** OLS Regression for Understanding Orientation.

```{r echo=FALSE, message=FALSE, warning=FALSE}
model1 <- lm(under ~ ses + sex + age_num + media + digital + social + interest + intercon + extef + intef + ope, data = merged_data)
summary(model1)
```

**Table 2** OLS Regression for Strategic Orientation.

```{r echo=FALSE, message=FALSE, warning=FALSE}
model2 <- lm(strate ~ ses + sex + age_num + media + digital + social + interest + intercon + extef + intef + ope, data = merged_data)
summary(model2)
```
**Figure 4** Coefplot for understanding orientation and strategic orientation.

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Assuming coef_df is already prepared as per previous instructions

# Update the extraction function to avoid spaces in names
get_coef <- function(model, model_name) {
  coefs <- summary(model)$coefficients
  data.frame(
    Term = rownames(coefs),
    Estimate = coefs[, "Estimate"],
    Std_Error = coefs[, "Std. Error"],  # Rename to 'Std_Error'
    Model = model_name
  )
}

# Apply the function to both models
coef_df1 <- get_coef(model1, "Model 1")
coef_df2 <- get_coef(model2, "Model 2")

# Combine the data frames and remove the intercept
coef_df <- rbind(coef_df1, coef_df2)
coef_df <- coef_df[coef_df$Term != "(Intercept)", ]

# Calculate 95% confidence intervals and determine significance
coef_df <- coef_df %>%
  mutate(
    Lower_CI = Estimate - 1.645 * Std_Error,  # Lower bound of the CI
    Upper_CI = Estimate + 1.645 * Std_Error,  # Upper bound of the CI
    Significant = if_else(Lower_CI > 0 & Upper_CI > 0 | Lower_CI < 0 & Upper_CI < 0, TRUE, FALSE)  
    )

# Create a mapping of old variable names to new names
name_mapping <- c(
  ses = "Socioeconomic Status",
  sex = "Gender",
  age_num = "Age",
  media = "Media Expo.",
  digital = "Dig, Media Expo.",
  social = "Soc. Media Expo.",
  interest = "Pol. Interest",
  intercon = "Interp. Conf.",
  extef = "Ext. Efficacy",
  intef = "Int. Efficacy",
  ope = "Onl. Efficacy"
)

# Apply the mapping to the dataframe
coef_df <- coef_df %>%
  mutate(Term = factor(Term, levels = names(name_mapping), labels = name_mapping))

# Define a dodge width for better separation
dodge_width <- 0.5

# Create the plot with updated names
ggplot(coef_df, aes(x = Term, y = Estimate, ymin = Lower_CI, ymax = Upper_CI, color = Model, group = Model)) +
  geom_pointrange(position = position_dodge(width = dodge_width), aes(size = Significant)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "orange") +
  theme_minimal() +
  labs(x = "Variables", y = "Estimated Coefficients") +
  coord_flip() +  # Flips the axes for better visualization of terms
  scale_color_manual(values = c("darkblue", "darkred"),
                     labels = c("Understanding", "Strategic")) +  # Set custom colors for each model
  scale_size_manual(values = c(0.5, 1.5), guide = FALSE) +  # Adjust line width based on significance
  theme(
    legend.position = "right",  # Hide the legend for line size
    axis.text.y = element_text(size = 8)  # Adjust text size if needed
  )
```

## Appendix

**Appendix 1** SEM for Understanding Orientation

```{r echo=FALSE, message=FALSE, warning=FALSE}
sem1 <- 'ope_a1 =~ ope1 + ope2 + ope3 + ope4
          intef_a1 =~ intef1 + intef2 + intef3
          extef_a1 =~ extef1 + extef2 + extef3
          interest_a1 =~ polint + procint + plebint
          media_a1 =~ tv + cable + newspaper + radio
          digital_a1 =~ tradonline + online + podcast + officialsm
          social_a1 =~ fb + insta + twitter + whatsapp + youtube + tiktok
          under_a1 =~ under_w3_1 + under_w3_2 + under_w3_3 + under_w3_4 + under_w3_5 + under_w3_6 + under_w3_7 + under_w3_8
          under_a1 ~ ses + sex + age_num + media_a1 + digital_a1 + social_a1 + interest_a1 + intercon + extef_a1 + intef_a1 + ope_a1'

fit_sem1 <- sem(sem1, data = merged_data)

summary(fit_sem1, fit.measures = TRUE, standardized = TRUE)

```
**Appendix 2** SEM for Strategic Orientation

```{r echo=FALSE, message=FALSE, warning=FALSE}
sem2 <- 'ope_a2 =~ ope1 + ope2 + ope3 + ope4
          intef_a2 =~ intef1 + intef2 + intef3
          extef_a2 =~ extef1 + extef2 + extef3
          interest_a2 =~ polint + procint + plebint
          media_a2 =~ tv + cable + newspaper + radio
          digital_a2 =~ tradonline + online + podcast + officialsm
          social_a2 =~ fb + insta + twitter + whatsapp + youtube + tiktok
          strate_a2 =~ strate_w3_1 + strate_w3_2 + strate_w3_3 + strate_w3_4 + strate_w3_5 + strate_w3_6 + strate_w3_7 + strate_w3_8
          strate_a2 ~ ses + sex + age_num + media_a2 + digital_a2 + social_a2 + interest_a2 + intercon + extef_a2 + intef_a2 + ope_a2'

fit_sem2 <- sem(sem2, data = merged_data)

summary(fit_sem2, fit.measures = TRUE, standardized = TRUE)
```


### Working with W1

```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}

data_justw1_na <- na.omit(data_w1[c("id", "polint", "procint", "plebint", "ope1", "ope2", "ope3", "ope4", "intef1", "intef2", "intef3", "extef1", "extef2", "extef3", "intercon", "tv", "cable", "newspaper", "radio", "tradonline", "online", "podcast", "officialsm","fb", "insta", "twitter", "whatsapp", "youtube", "tiktok", "age_num", "ses", "sex", "educ", "under1", "under2", "under3", "under4", "strate1", "strate2", "strate3", "strate4")])
sum(is.na(data_justw1_na))

data_justw1_na <- data_justw1_na %>%
  mutate(across(where(is.labelled), as.numeric))

cfa.model_w1_1 <- 'ope_1 =~ ope1 + ope2 + ope3 + ope4
              intef_1 =~ intef1 + intef2 + intef3
              extef_1 =~ extef1 + extef2 + extef3
              interest_1 =~ polint + procint + plebint'
cfa.model_w1_2 <- 'media_1 =~ tv + cable + newspaper + radio
              digital_1 =~ tradonline + online + podcast + officialsm
              social_1 =~ fb + insta + twitter + whatsapp + youtube + tiktok'
cfa.model_w1_3 <- 'under_1 =~ under1 + under2 + under3 + under4
              strate_1 =~ strate1 + strate2 + strate3 + strate4'

fit_cfa_w1_1 <- cfa(cfa.model_w1_1, data = data_justw1_na)
latent_scores_w1_1 <- predict(fit_cfa_w1_1)

fit_cfa_w1_2 <- cfa(cfa.model_w1_2, data = data_justw1_na)
latent_scores_w1_2 <- predict(fit_cfa_w1_2)

fit_cfa_w1_3 <- cfa(cfa.model_w1_3, data = data_justw1_na)
latent_scores_w1_3 <- predict(fit_cfa_w1_3)

data_justw1_na <- cbind(data_justw1_na, latent_scores_w1_1, latent_scores_w1_2, latent_scores_w1_3)
```

**Appendix 3**. OLS for Understanding Orientation just using W1.

```{r echo=FALSE, message=FALSE, warning=FALSE}
model1_w1 <- lm(under_1 ~ ses + sex + age_num + media_1 + digital_1 + social_1 + interest_1 + intercon + extef_1 + intef_1 + ope_1, data = data_justw1_na)
summary(model1_w1)
```

**Appendix 4**. OLS for Strategic Orientation just using W1.
```{r echo=FALSE, message=FALSE, warning=FALSE}
model2_w1 <- lm(strate_1 ~ ses + sex + age_num + media_1 + digital_1 + social_1 + interest_1 + intercon + extef_1 + intef_1 + ope_1, data = data_justw1_na)
summary(model2_w1)
```

**Appendix 5**. OLS for Strategic Orientation just using W1, no factor.
```{r echo=FALSE, message=FALSE, warning=FALSE}

model2_1 <- lm(strate1 ~ ses + sex + age_num + media_1 + digital_1 + social_1 + interest_1 + intercon + extef_1 + intef_1 + ope_1, data = data_justw1_na)
summary(model2_1)
model2_2 <- lm(strate2 ~ ses + sex + age_num + media_1 + digital_1 + social_1 + interest_1 + intercon + extef_1 + intef_1 + ope_1, data = data_justw1_na)
summary(model2_2)
model2_3 <- lm(strate3 ~ ses + sex + age_num + media_1 + digital_1 + social_1 + interest_1 + intercon + extef_1 + intef_1 + ope_1, data = data_justw1_na)
summary(model2_3)
model2_4 <- lm(strate4 ~ ses + sex + age_num + media_1 + digital_1 + social_1 + interest_1 + intercon + extef_1 + intef_1 + ope_1, data = data_justw1_na)
summary(model2_4)

```

```{r echo=FALSE, message=FALSE, warning=FALSE}

# Apply the function to both models
coef_strate1 <- get_coef(model2_1, "Model S1")
coef_strate2 <- get_coef(model2_2, "Model S2")
coef_strate3 <- get_coef(model2_3, "Model S3")
coef_strate4 <- get_coef(model2_4, "Model S4")

# Combine the data frames and remove the intercept
coef_strate <- rbind(coef_strate1, coef_strate2, coef_strate3, coef_strate4)
coef_strate <- coef_strate[coef_strate$Term != "(Intercept)", ]

# Calculate 95% confidence intervals and determine significance
coef_strate <- coef_strate %>%
  mutate(
    Lower_CI = Estimate - 1.645 * Std_Error,  # Lower bound of the CI
    Upper_CI = Estimate + 1.645 * Std_Error,  # Upper bound of the CI
    Significant = if_else(Lower_CI > 0 & Upper_CI > 0 | Lower_CI < 0 & Upper_CI < 0, TRUE, FALSE)
  )

# Create a mapping of old variable names to new names
name_mapping_1 <- c(
  ses = "Socioeconomic Status",
  sex = "Gender",
  age_num = "Age",
  media_1 = "Media Expo.",
  digital_1 = "Dig, Media Expo.",
  social_1 = "Soc. Media Expo.",
  interest_1 = "Pol. Interest",
  intercon = "Interp. Conf.",
  extef_1 = "Ext. Efficacy",
  intef_1 = "Int. Efficacy",
  ope_1 = "Onl. Efficacy"
)

# Apply the mapping to the dataframe
coef_strate <- coef_strate %>%
  mutate(Term = factor(Term, levels = names(name_mapping_1), labels = name_mapping_1))

# Define a dodge width for better separation
dodge_width <- 0.5

# Create the plot with updated names
ggplot(coef_strate, aes(x = Term, y = Estimate, ymin = Lower_CI, ymax = Upper_CI, color = Model, group = Model)) +
  geom_pointrange(position = position_dodge(width = dodge_width)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "orange") +
  theme_minimal() +
  labs(x = "Variables", y = "Estimated Coefficients") +
  coord_flip() +  # Flips the axes for better visualization of terms
  scale_color_manual(
    values = c("darkblue", "darkred","darkgreen", "purple"),
    labels = c("Talk if I win", "Form is more important", "Not express what I think", "Agreements waste of time")) +  # Set custom colors for each model
  scale_size_manual(values = c(0.5, 1.5), guide = FALSE) +  # Adjust line width based on significance
  theme(
    legend.position = "right",
    axis.text.y = element_text(size = 8)  # Adjust text size if needed
  )
```

### Alternative models, by adding observable variables.

```{r echo=FALSE, message=FALSE, warning=FALSE}
data_justw1_na$undersum <- (data_justw1_na$under1+data_justw1_na$under2+data_justw1_na$under3+data_justw1_na$under4)/4
data_justw1_na$stratesum <- (data_justw1_na$strate1+data_justw1_na$strate2+data_justw1_na$strate3+data_justw1_na$strate4)/4

data_justw1_na$mediasum <- (data_justw1_na$tv+data_justw1_na$cable+data_justw1_na$newspaper+data_justw1_na$radio)/4
data_justw1_na$digitalsum <-(data_justw1_na$tradonline+data_justw1_na$online+data_justw1_na$podcast+data_justw1_na$officialsm)/4
data_justw1_na$socialsum <- (data_justw1_na$fb+data_justw1_na$insta+data_justw1_na$twitter+data_justw1_na$whatsapp+data_justw1_na$youtube+data_justw1_na$tiktok)/6

data_justw1_na$extefsum <- (data_justw1_na$extef1+data_justw1_na$extef2+data_justw1_na$extef3)/3
data_justw1_na$intefsum <- (data_justw1_na$intef1+data_justw1_na$intef2+data_justw1_na$intef3)/3
data_justw1_na$opesum <- (data_justw1_na$ope1+data_justw1_na$ope2+data_justw1_na$ope3+data_justw1_na$ope4)/4

```

**Appendix 6**. OLS for Understanding Orientation and Strategic Orientation just using W1 and by adding observable variebles (not CFA).

```{r echo=FALSE, message=FALSE, warning=FALSE}
model_a1 <- lm(undersum ~ ses + sex + age_num + mediasum + digitalsum + socialsum + polint + intercon + extefsum + intefsum + opesum, data = data_justw1_na)
summary(model_a1)

model_a2 <- lm(stratesum ~ ses + sex + age_num + mediasum + digitalsum + socialsum + polint + intercon + extefsum + intefsum + opesum, data = data_justw1_na)
summary(model_a2)
```

